\plaintitle

### 2018-04-03 paper/paper.tex
昔の論文からコピー中

\section{Related Works}

>>>>

\section{Related Work}

\subsection{Intelligent help systems}

There have been tremendous amount of researches on intelligent help systems\cite{Delisle:2002:UIH:606412.606415},
but few number of projects seem to be going on these days,
maybe because now we can use the Internet for getting intelligent help from
real people.
Information on the net is really rich these days, and we can easily
find somebody who can answer questions intelligently.
This is a very good news, but 
asking many trivial questions on the net is not considered to be a
good manner, and
using a powerful and flexible local help system like ExpandHelp is
preferable before asking other people.
